### 2021-07-19 doc/thesis/chapters/system-design-process.tex
re-evaluate

>>>>

The re-evaluate step is a central building block in the SIMILAR concept.
All of the other steps have a connection to it, in the form of a feedback loop.
However, depending on the nature of the project and the point in the timeline of its life cycle, not all of these loops may be exercised all the time.
The idea of re-evaluation and the subsequent improvement of a process is a widely applied and well-known concept.
Its main function is to observe an output and to use this information to improve the systems' input.
